A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Use Chan rather than MVar for state example; be clearer about errors there.

type Recipient = (SessionID, CC.MVar String)
type RcptList = CC.MVar [Recipient]
\end{code}

@@

\begin{code}
srvSend :: Server RcptList -> String -> Server ()
srvSend remoteRcpts message = do
    rcpts <- remoteRcpts
    liftIO $ do
      recipients <- CC.readMVar rcpts
      mapM_ (CC.forkIO . deliver message) recipients
  where
    deliver msg (_,rcptMVar) = CC.putMVar rcptMVar msg
\end{code}

The send function is slightly more complex. The incoming message is written to
the \lstinline!MVar! corresponding to each active session. Note the use of
\lstinline!forkIO!. Some recipients may be slow to empty their \lstinline!MVar!
to make room for a new message. In this case, we don't want to force all
recipients to wait for the slowest one, so we spawn a new lightweight thread
to handle delivery for each recipient.

\begin{code}
srvAwait :: Server RcptList -> Server String
srvAwait remoteRcpts = do
  rcpts <- remoteRcpts
  sid <- getSessionID
  liftIO $ do
    recipients <- CC.readMVar rcpts
    case lookup sid recipients of
      Just mv -> CC.takeMVar mv
      _       -> fail "Unregistered session!"
\end{code}

The final server operation, notifying users of pending messages, finds the
appropriate \lstinline!MVar! to wait on by searching the recipient list for the
session identifier of the calling user, and then blocks until a message arrives
in said \lstinline!MVar!. This is a little different from the other two
operations, which perform their work as quickly as possible and then return
immediately.

If the caller's session identifier could not be found in the
recipient list, it has for some reason not completed its handshake with the
server. If this is the case, we simply drop the session by throwing an error;
the session will be automatically cleaned up on the server side and an exception
is thrown to the client.

>>>>

type Recipient = (SessionID, CC.Chan String)
type RcptList = CC.MVar [Recipient]
\end{code}

@@

\begin{code}
srvSend :: Server RcptList -> String -> Server ()
srvSend remoteRcpts message = do
    rcpts <- remoteRcpts
    liftIO $ do
      recipients <- CC.readMVar rcpts
      mapM_ (\rcpt -> writeChan rcpt message) recipients
\end{code}

The send function is slightly more complex. The incoming message is written to
the \lstinline!Chan! corresponding to each active session.

\begin{code}
srvAwait :: Server RcptList -> Server String
srvAwait remoteRcpts = do
  rcpts <- remoteRcpts
  sid <- getSessionID
  liftIO $ do
    recipients <- CC.readMVar rcpts
    case lookup sid recipients of
      Just mv -> CC.readChan mv
      _       -> fail "Unregistered session!"
\end{code}

The final server operation, notifying users of pending messages, finds the
appropriate \lstinline!Chan! to wait on by searching the recipient list for the
session identifier of the calling user, and then blocks until a message arrives
in said \lstinline!MVar!. This is a little different from the other two
operations, which perform their work as quickly as possible and then return
immediately.

If the caller's session identifier could not be found in the
recipient list, it has for some reason not completed its handshake with the
server. If this is the case, we simply drop the session by throwing an error;
an exception will be thrown to the client. No server side state needs to be
cleaned up as the very lack of such state was our reason for dropping the
session.
